A novel 1000\,\,MW double-reheat ultra supercritical system with turbine-extraction-heated air preheaters and low temperature economizers

### 2018-01-30 article.tex
完成了系统和子系统用分析，对论文需要添加部分进行了中文注释

\renewcommand{\nomgroup}[1]
{%
\ifthenelse{\equal{#1}{C}}{\item[\textbf{Constants}]}{%
\ifthenelse{\equal{#1}{V}}{\item[\textbf{Variables}]}{%
\ifthenelse{\equal{#1}{S}}{\item[\textbf{sets}]}{}}}
}
\makenomenclature

@@

\begin{abstract}
Herein, an novel system of a 1000\,\,MW double-reheat ultra-supercritical (USC) unit with turbine-extraction-heated air preheaters (EAPHs), which use turbine extractions as heat sources of air preheaters while economizer outlet flue gas’ heat absorbed by low pressure economizers (LPEs), is designed based on reference system of a 1000\,\,MW double-reheat USC unit. 
The energetic performance analyses of the novel system and reference system are used to compare their major parameters. 
In addition, thermodynamic analyses under partial load operation conditions are presented. 
The results show that the proposed novel system reduced the exergy destruction in the air-heating processes. Furthermore, the novel system increases the temperature of secondary air and reduces the overall superheat degree of several extractions.
 Theoretically, the novel system reduces the SCE consumption by nearly 5.5\,g/kWh under THA load when the temperature of the flue gas entering the electrostatic precipitator is set to 95$^\circ$C.
 Moreover, the novel system can still has advantages in coal saving under partial load condition.
 Our findings indicate that system with EAPH could improves the performance of the unit and may provide a theoretical basis for the novel of double-reheat USC units.
\end{abstract}

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=1\textwidth]{fig/reference_system}
\caption{Schematic of the reference system} 
\label{fig:reference_system}
\end{figure}
%从参考系统的锅炉虽然仍然采用Π型布置，但其内部受热面和传统一次再热锅炉有较大区别。
Furnace layout shown in Fig~\ref{fig:boiler_surface}, the boiler furnace is composited by the membrane wall, along flue gas flow direction lays low-temperature superheater (Lts) screen tube, cold segment of high-temperature ﬁrst reheater (Csf), cold segment of high-temperature second reheater (Csf), High temperature super-heater (Hts), hot segment of high-temperature ﬁrst reheater (Hsf), hot segment of high-temperature second reheater (Hss).
After Hsf and Hss the flue gas channel is divided into the front-duct flue and the back-duct flue. The front duct arranges low-temperature first reheater (Ltfr) and the front-duct economizerz (中，而水平烟道和竖井烟道中仅布置有空气预热设备。所以锅炉可以分成两部分:炉膛内完成水/蒸汽吸热的boiler，和尾部烟道内 完成空气预热的APH。
\begin{figure}[htbp]
\centering
\includegraphics[width=0.5\textwidth]{fig/boiler_surface}
\caption{Boiler internal heat exchangers layout} 
\label{fig:boiler_surface}
\end{figure}
Feco), the back duct arranges a low-temperature second reheater (Ltsr) and back-duct economizer (Beco). The rear flue is equipped with an air preheater(APH).
% 从锅炉受热面布置可以看出，锅炉主要受热面布置在炉膛之

@@

Compared with the air preheater, the regenerative heaters have lower logarithm mean temperature difference (LMTD).
However, it is found that the temperature difference between the hot and cold stream at the inlet high temperature regenerative heaters is also relatively large, which causes irreversible loss. To reduce the superheat degree of the 2nd and 4th extractions and to heat feedwater, two additional outer steam coolers are installed.
Results show that the inlet temperature difference of HRH2 and HRH4 is greatly reduced, and the exergy efficiency is improved correspondingly.
However, the inlet temperature difference between the cold and hot stream of other high temperature regenerative heaters remains very high.
Moreover, because of the material restriction of the water wall, the temperature of feedwater at the inlet of boiler is restricted to 315$^\circ$C. 
In the reference system, the first extraction has to be throttled to ensure the temperature of feedwater not exceeding the restriction.
The pressure of the first extraction is throttled from 106.70 bar to 88.56 bar, and the temperature is decreased from 425.60$^\circ$C to 413.77$^\circ$C. The throttling of the first extraction will certainly cause extra irreversible loss.
\subsection{Proposal of a novel system with EAPH and LPE}
\label{sub2:prop novel sys}

The  layout of the optimization system is presented in Fig~\ref{fig:novel_system}.
In the optimization system, the air is not heated by flue gas in the conventional air preheater, and 8 new air preheaters (APH1\-APH8) using several extractions to heat the air is adopted.
The new air preheater is similar with regenerative heaters in function.
As shown in Fig~ the extracted steam is sent to the regenerative heater to heat the condensate or feedwater, and then the drainage from the air preheater joins with that of corresponding regenerative heater.
It should be mentioned that not all the extractions are available for air heating
For the last two stage extractions, their pressure is much lower than barometric pressure which makes it extremely difficult to maintain such low pressure environment inside the heat exchangers, and APH8 shall be shut down under low load for the same reason.
Besides, to reduce the superheat degree of extractions entering the heat exchangers and to improve the air temperature, four additional outer steam coolers (AOC1- AOC4) are installed at the outlet of APH1.
Since extractions from the 2nd to the 5th have superheat degree, they are sent to AOCs in the order of temperature level.
For example, the 2nd extraction has the highest temperature, and is applied to heat the air in the 1st AOC, and then the cooled steam from AOC1 is sent to HRH2 and air APH2 to heat the water and air respectively.

@@

\subsection{Model establish method and main assumption}
\label{ssub3:modle description}
\textcolor{red}{!novel model established based on the reference which parameters change and which not! }
%对模型中如何基于现有系统进行的改造，和哪些数据不发生变化进行说明
In this paper, the thermodynamic cycle of the thermal system under different loads are simulated with EBSILON® Professional for its flexibility and level of detail. 
EBSILON is a power plant simulation tool which can calculate thermodynamic quantities. 
The simulation model gives the detailed data with high degree of reliability to calculate the thermodynamic state.
EBSIOLON's simulation and parameter calculation of the equipment is based on experimental characteristics of units during the process of modeling design and off-design conditions.
However, only some characteristic curves of turbine can actually be obtained, while boiler and heat exchanger data cannot be obtained, which can only use the system built-in data as an alternative.
It’s needed to assume that the difference between the built-in data and the actual data to meet the error requirements.
The following assumptions need to be made in order to be able to simulate correctly.
\begin{enumerate}[(1)]
\item Both novel and reference systems are operated in stable condition.
\item The thermal efficiency of the equipment is calculated from the thermal balance of the input and output parameters of the components, assuming that the calculation error requirement can be met.
\item According to the heat map, set the upper and lower end difference of the heat exchanger as a fixed value, and do not change among different condition.
\item  Do not take the pips' complexity and equipment’s installation difficulty of the novel system as consideration.
\end{enumerate}

\subsection{Thermodynamic metric} %(fold)
\label{ssub3:analsys method} 
%为了能够对优化系统与参考系统进行评估，揭示系统优化的内在机理，本文引入热力学第二定律的分析方法即用分析方法。
Exergy analysis, is adopted to reveal the location, the magnitude and the sources of thermodynamic inefficiencies of the unit.
Usually, exergy destruction and exergy efficiency are chosen as evaluation indices of the thermal system or an individual component, 
The general exergy balance of component can be expressed in the following form:
\begin{equation}
\label{equation:1}
\dot{I}=\sum\dot{E}{}_{in}-\sum\dot{E}{}_{out}+\sum\dot{W}{}_{in}-\sum\dot{W}{}_{out}
\end{equation}
\nomenclature[Cp]{$E$}{The number of angels per unit area}%

\nomenclature[Vo]{$W$}{The number of angels per needle point}%

\nomenclature[so]{$I$}{The area of the needle point}%

@@

\section{Thermodynamic performance evaluation} % (fold)
\label{sub:Thermodynamic_evaluation}
%对word版本的分布进行了较大的改动，需要继续调节
\subsection{Thermodynamic comparison in design condition}
\label{ssub:desing_compare}
%表四
The comparison of thermal dynamic performance between these two systems is given in Table~\ref{table:thermal performance compare}. 
Under design condition, the novel system brings an improvement of net generating power by 11.02 MW, and a reduction of SCE consumption by 5.5\,g/kWh.
The power generation efficiency reaches 48.73\%, 1.04\% higher then that of reference system.
Meanwhile, the exergy efficiency of novel system is 1.01\% higher, showing good exergy-saving effect.

\begin{table}
\caption{Thermodynamic performance of reference and novel systems}
\label{table:thermal performance compare}
\centering
\begin{tabular}{p{7.5cm}p{1.75cm}p{1.75cm}}
\toprule 
Items & Reference system & Novel system\tabularnewline
\midrule
Net generating power (MW) & 999.10 & 1011.19\tabularnewline
Generating efficiency (\%) & 47.69 & 48.73\tabularnewline
Addition in generating efficiency (\%) &  & 1.04\tabularnewline
Standard coal consumption rate (g/kWh) & 257.59 & 252.10\tabularnewline
Reduction in standard coal consumption rate (g/kWh) &  & 5.49\tabularnewline
Exergy efficiency (\%) & 46.51 & 47.52\tabularnewline
Addition in exergy efficiency (\%) &  & 1.01\tabularnewline
\bottomrule
\end{tabular}
\end{table}
% 根据用损失对比表从新进行分析，从为什么锅炉空预器效率提高，其他不变或者降低说起
Table~\ref{table:system exergy campare} gives the results of subsystem exergy analysis of the two system. 
It is found that the novel system has an improvement in exergetic performance by an decrease of 10.82\,MW of total exergy destruction rate.
Exergy destruction rate of boiler accounts for the highest proportion and decrease most (11.04\,MW).
Air preheat subsystem's exergy destruction rate of novel system changes from 27.39\,MW to 16.55\,MW, having a 10.84\,MW decreasmen
 Results show that the exergy destruction of boiler is 855.72 MW, leading to the increment of exergy efficiency by 0.18\%. In addition, there is almost no change of the exergy parameters of the steam turbines, generator and condenser. 
 For the air heating system and regenerative system, great change happens compared with the formal system, and detailed analysis will be carried out next.

Through the analysis of the reference system and the optimization system, it can be seen that the exergy efficiency of the optimization system is improved and the exergy destruction is reduced.
Comparing the proportion of different components in the total exergy destruction between the two systems, we can see that in addition to the turbine, the exergy destruction of all components is reduced. 
Among them, the air preheating system efficiency is the most obviously improved，to 38.94\%.

@@

>>>>

\renewcommand{\nomgroup}[1]
{%Mathematical symbols
\ifthenelse{\equal{#1}{G}}{\item[\textbf{Greek letters}]}{%
\ifthenelse{\equal{#1}{S}}{\item[\textbf{Subscripts}]}{%
\ifthenelse{\equal{#1}{U}}{\item[\textbf{Superscripts}]}{
\ifthenelse{\equal{#1}{C}}{\item[\textbf{Constants}]}{
\ifthenelse{\equal{#1}{M}}{\item[\textbf{Mathematical symbols}]}{
}%几个类别需要几个括号
}
}
}
}%几个类别需要几个括号
}%对应1]
\makenomenclature

@@

\begin{abstract}%修改到300字以内
Herein, an novel system of a 1000\,\,MW double-reheat ultra-supercritical (USC) unit with turbine-extraction-heated air preheaters (EAPHs), which use turbine extractions as heat sources of air preheaters while economizer outlet flue gas’ heat absorbed by low pressure economizers (LPEs), is designed based on reference system of a 1000\,\,MW double-reheat USC unit. 
The energetic performance analyses of the novel system and reference system are used to compare their major parameters. 
In addition, thermodynamic analyses under partial load operation conditions are presented. 
The results show that the proposed novel system reduced the exergy destruction in the air-heating processes. Furthermore, the novel system increases the temperature of secondary air and reduces the overall superheat degree of several extractions.
 Theoretically, the novel system reduces the SCE consumption by nearly 5.5\,g/kWh under THA load when the temperature of the flue gas entering the electrostatic precipitator is set to 95$^\circ$C.
 Moreover, the novel system can still has advantages in coal saving under partial load condition.
 Our findings indicate that system with EAPH could improves the performance of the unit and may provide a theoretical basis for the novel of double-reheat USC units.
\end{abstract}

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=1\textwidth]{fig/reference_system}
\caption{Schematic of the reference system} 
\label{fig:reference_system}
\end{figure}
%从参考系统的锅炉虽然仍然采用Π型布置，但其内部受热面和传统一次再热锅炉有较大区别。
Furnace layout shown in Fig~\ref{fig:boiler_surface}, the boiler furnace is composited by the membrane wall, along flue gas flow direction lays low-temperature superheater (Lts) screen tube, cold segment of high-temperature ﬁrst reheater (Csf), cold segment of high-temperature second reheater (Csf), High temperature super-heater (Hts), hot segment of high-temperature ﬁrst reheater (Hsf), hot segment of high-temperature second reheater (Hss).
After Hsf and Hss the flue gas channel is divided into the front-duct flue and the back-duct flue. The front duct arranges low-temperature first reheater (Ltfr) and the front-duct economizerz 
(%中，而水平烟道和竖井烟道中仅布置有空气预热设备。所以锅炉可以分成两部分:炉膛内完成水/蒸汽吸热的boiler，和尾部烟道内 完成空气预热的APH。Feco), the back duct arranges a low-temperature second reheater (Ltsr) and back-duct economizer (Beco). The rear flue is equipped with an air preheater(APH).
% 从锅炉受热面布置可以看出，锅炉主要受热面布置在炉膛之
\begin{figure}[htbp]
\centering
\includegraphics[width=0.5\textwidth]{fig/boiler_surface}
\caption{Boiler internal heat exchangers layout} 
\label{fig:boiler_surface}
\end{figure}

@@

Compared with the air preheater, the regenerative heaters have lower logarithm mean temperature difference (LMTD).
However, it is found that the temperature difference between the hot and cold stream at the inlet high temperature regenerative heaters is also relatively large, which causes irreversible loss. To reduce the superheat degree of the 2nd and 4th extractions and to heat feedwater, two additional outer steam coolers are installed.
Results show that the inlet temperature difference of HRH2 and HRH4 is greatly reduced, and the exergy efficiency is improved correspondingly.
However, the inlet temperature difference between the cold and hot stream of other high temperature regenerative heaters remains very high.
Moreover, because of the material restriction of the water wall, the temperature of feedwater at the inlet of boiler is restricted to 315$^\circ$C. 
In the reference system, the first extraction has to be throttled to ensure the temperature of feedwater not exceeding the restriction.
The pressure of the first extraction is throttled from 106.70 bar to 88.56 bar, and the temperature is decreased from 425.60$^\circ$C to 413.77$^\circ$C. The throttling of the first extraction will certainly cause extra irreversible loss.
\subsection{Proposal of a novel system with EAPH and LPE}
\label{sub2:prop novel sys}
%添加为什么进行这种设计的解释，为什么设置LPE AOC APH的级数
The  layout of the optimization system is presented in Fig~\ref{fig:novel_system}.
In the optimization system, the air is not heated by flue gas in the conventional air preheater, and 8 new air preheaters (APH1\-APH8) using several extractions to heat the air is adopted.
The new air preheater is similar with regenerative heaters in function.
As shown in Fig~ the extracted steam is sent to the regenerative heater to heat the condensate or feedwater, and then the drainage from the air preheater joins with that of corresponding regenerative heater.
It should be mentioned that not all the extractions are available for air heating
For the last two stage extractions, their pressure is much lower than barometric pressure which makes it extremely difficult to maintain such low pressure environment inside the heat exchangers, and APH8 shall be shut down under low load for the same reason.
Besides, to reduce the superheat degree of extractions entering the heat exchangers and to improve the air temperature, four additional outer steam coolers (AOC1- AOC4) are installed at the outlet of APH1.
Since extractions from the 2nd to the 5th have superheat degree, they are sent to AOCs in the order of temperature level.
For example, the 2nd extraction has the highest temperature, and is applied to heat the air in the 1st AOC, and then the cooled steam from AOC1 is sent to HRH2 and air APH2 to heat the water and air respectively.

@@

\subsection{Model establish method and main assumption}
\label{ssub3:modle description}
\textcolor{red}{!novel model established based on the reference which parameters change and which not! }
%对模型中如何基于现有系统进行的改造，和哪些数据不发生变化进行说明
%添加模型中基本部件的特性 添加个表格
In this paper, the thermodynamic cycle of the thermal system under different loads are simulated with EBSILON® Professional for its flexibility and level of detail. 
EBSILON is a power plant simulation tool which can calculate thermodynamic quantities. 
The simulation model gives the detailed data with high degree of reliability to calculate the thermodynamic state.
EBSIOLON's simulation and parameter calculation of the equipment is based on experimental characteristics of units during the process of modeling design and off-design conditions.
However, only some characteristic curves of turbine can actually be obtained, while boiler and heat exchanger data cannot be obtained, which can only use the system built-in data as an alternative.
It’s needed to assume that the difference between the built-in data and the actual data to meet the error requirements.
The following assumptions need to be made in order to be able to simulate correctly.
\begin{enumerate}[(1)]
\item Both novel and reference systems are operated in stable condition.
\item The thermal efficiency of the equipment is calculated from the thermal balance of the input and output parameters of the components, assuming that the calculation error requirement can be met.
\item According to the heat map, set the upper and lower end difference of the heat exchanger as a fixed value, and do not change among different condition.
\item  Do not take the pips' complexity and equipment’s installation difficulty of the novel system as consideration.
\end{enumerate}

\subsection{Thermodynamic metric} %(fold)
\label{ssub3:analsys method} 
%为了能够对优化系统与参考系统进行评估，揭示系统优化的内在机理，本文引入热力学第二定律的分析方法即用分析方法。
Exergy analysis, is adopted to reveal the location, the magnitude and the sources of thermodynamic inefficiencies of the unit.
Usually, exergy destruction and exergy efficiency are chosen as evaluation indices of the thermal system or an individual component, 
The general exergy balance of component can be expressed in the following form:
\begin{equation}
\label{equation:1}
\dot{I}=\sum\dot{E}{}_{in}-\sum\dot{E}{}_{out}+\sum\dot{W}{}_{in}-\sum\dot{W}{}_{out}
\end{equation}

@@

\section{Thermodynamic performance evaluation} % (fold)
\label{sub:Thermodynamic_evaluation}
%对word版本的分布进行了较大的改动，需要继续调节
\subsection{Thermodynamic comparison in design condition}
\label{ssub:desing_compare}
%表四
The comparison of thermal dynamic performance between these two systems is given in Table~\ref{table:thermal performance compare}. 
Under design condition, the novel system brings an improvement of net generating power by 11.02 MW, and reduces SCE consumption by 5.5\,g/kWh.
The power generation efficiency reaches 48.73\%, 1.04\% higher then that of reference system.
Meanwhile, the exergy efficiency of novel system is 1.01\% higher, showing good exergy-saving effect.

\begin{table}
\caption{Thermodynamic performance of reference and novel systems}
\label{table:thermal performance compare}
\centering
\begin{tabular}{p{7.5cm}p{1.75cm}p{1.75cm}}
\toprule 
Items & Reference system & Novel system\tabularnewline
\midrule
Net generating power (MW) & 999.10 & 1011.19\tabularnewline
Generating efficiency (\%) & 47.69 & 48.73\tabularnewline
Addition in generating efficiency (\%) &  & 1.04\tabularnewline
Standard coal consumption rate (g/kWh) & 257.59 & 252.10\tabularnewline
Reduction in standard coal consumption rate (g/kWh) &  & 5.49\tabularnewline
Exergy efficiency (\%) & 46.51 & 47.52\tabularnewline
Addition in exergy efficiency (\%) &  & 1.01\tabularnewline
\bottomrule
\end{tabular}
\end{table}
% 根据用损失对比表从新进行分析，从为什么锅炉空预器效率提高，其他不变或者降低说起
Table~\ref{table:system exergy campare} gives the results of subsystem exergy analysis of the two system. 
It is found that the novel system has an improvement in exergetic performance by an decrease of 10.82\,MW of total exergy destruction rate.
Exergy destruction rate of boiler accounts for the highest proportion and decrease most (11.04\,MW).
Air preheat subsystem's exergy destruction rate changes from 27.39\,MW to 16.55\,MW, having a 10.84\,MW decrement, having the largest Optimization ratio.
In the mean time, turbines and regenerative subsystem have a relatively small change at about 1\,MW.

The item "other" of novel system is higher then reference system, showing that the uncalculated components of systems have a increment of exergy destruction rate.
Among the uncalculated components, the pips' amount increasing and work fluid mixing with parameters not match are the mainly reason why that party has a increment in exergy destruction rate.

@@

\nomenclature[M]{$\dot{I}$}{Exergy destruction rate (MW)}%
\nomenclature[S]{$in$}{inlet}%
\nomenclature[S]{$out$}{outlet}%
\nomenclature{AOC}{additional outer steam cooler}
